|

### 2023-05-01 manuscript/paper.Rmd
Added my affiliation. CDSC!

---
title: |
  |  \Large Stickle!
author: | 
  | \large Matthew Stuart \vspace{-1.1mm}
  | \normalsize Department of Mathematics and Statistics \vspace{-1mm}
  | \normalsize Loyola University Chicago \vspace{-1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1mm}
  | \normalsize [`mstuart@luc.edu`](mailto:mstuart@luc.edu) \vspace{-1mm}
  |
  | \large Akhil Ghosh \vspace{-1.1mm}
  | \normalsize Department of Mathematics and Statistics \vspace{-1mm}
  | \normalsize Loyola University Chicago \vspace{-1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1mm}
  | \normalsize [`aghosh@luc.edu`](mailto:aghosh@luc.edu) \vspace{-1mm}
  |
  | \large Yoel Stuart \vspace{-1.1mm}
  | \normalsize Department of Biology \vspace{-1mm}
  | \normalsize Loyola University Chicago \vspace{-1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1mm}
  | \normalsize [`ystuart@luc.edu`](mailto:ystuart@luc.edu) \vspace{-1mm}
  |
  | \large Gregory J. Matthews \vspace{-1.1mm}
  | \normalsize Department of Mathematics and Statistics \vspace{-1mm}
  | \normalsize Loyola University Chicago \vspace{-1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1mm}
  | \normalsize [`gmatthews1@luc.edu`](mailto:gmatthews1@luc.edu) \vspace{-1mm}
abstract: |
  | Evewryone loves the stickle \vspace{2mm}
  | *Keywords*: Stickle
bibliography: references.bib
fontsize: 12pt
link-citations: true
linkcolor: cyan
urlcolor: cyan
output:
  pdf_document:
    df_print: kable
    number_sections: true
    keep_tex: true
header-includes:
 \usepackage{setspace}
 \setstretch{1.15}
 \usepackage{float}
 \floatplacement{figure}{t}
---

@@

$$
X_{gti} \sim N(\mu_{gt}, \sigma^2)\\

\mu_{gt} \sim \kappa \mu_{g(t-1)} + (1-\kappa)\theta_g + \nu_{gt}\\

\nu_{gt} \sim N(0,\tau^2)\\
$$
Priors: 
$$
\sigma^2 \sim Scaled-Inv \chi^2(1)\\
\tau^2 \sim Scaled-Inv \chi^2(1)\\

\mu_{g0} \sim N(0,10000000000000), g = 1,2\\

\kappa \sim N(0,10000000000)\\
\theta \sim N(0,10000000000) \\

$$

>>>>

---
title: |
  |  \Large Stickle!
author: | 
  | \large Matthew Stuart \vspace{-1.1mm}
  | \normalsize Department of Mathematics and Statistics \vspace{-1mm}
  | \normalsize Loyola University Chicago \vspace{-1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1mm}
  | \normalsize [`mstuart@luc.edu`](mailto:mstuart@luc.edu) \vspace{-1mm}
  |
  | \large Akhil Ghosh \vspace{-1.1mm}
  | \normalsize Department of Mathematics and Statistics \vspace{-1mm}
  | \normalsize Loyola University Chicago \vspace{-1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1mm}
  | \normalsize [`aghosh@luc.edu`](mailto:aghosh@luc.edu) \vspace{-1mm}
  |
  | \large Yoel Stuart \vspace{-1.1mm}
  | \normalsize Department of Biology \vspace{-1mm}
  | \normalsize Loyola University Chicago \vspace{-1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1mm}
  | \normalsize [`ystuart@luc.edu`](mailto:ystuart@luc.edu) \vspace{-1mm}
  |
  | \large Gregory J. Matthews \vspace{-1.1mm}
  | \normalsize Center for Data Science and Consulting; Department of Mathematics and Statistics \vspace{-1mm}
  | \normalsize Loyola University Chicago \vspace{-1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1mm}
  | \normalsize [`gmatthews1@luc.edu`](mailto:gmatthews1@luc.edu) \vspace{-1mm}
abstract: |
  | Evewryone loves the stickle \vspace{2mm}
  | *Keywords*: Stickle
bibliography: references.bib
fontsize: 12pt
link-citations: true
linkcolor: cyan
urlcolor: cyan
output:
  pdf_document:
    df_print: kable
    number_sections: true
    keep_tex: true
header-includes:
 \usepackage{setspace}
 \setstretch{1.15}
 \usepackage{float}
 \floatplacement{figure}{t}
---

@@

$$
X_{gti} \sim N(\mu_{gt}, \sigma^2)
$$
$$
\mu_{gt} \sim \kappa \mu_{g(t-1)} + (1-\kappa)\theta_{g} + \nu_{gt}
$$
$$
\nu_{gt} \sim N(0,\tau^2)
$$
Priors: 
$$
\sigma^2 \sim Scaled-Inv \chi^2(1)
$$
$$
\tau^2 \sim Scaled-Inv \chi^2(1)
$$
$$
\mu_{g0} \sim N(0,10000000000000), g = 1,2\\
$$
$$
\kappa \sim N(0,10000000000)\\
$$
$$
\theta \sim N(0,10000000000) \\
$$
